

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Qijun Tong} \\[7.5pt]
\href{https://github.com/QijunTong0}{\raisebox{-0.05\height}\faGithub\ QijunTong0} \ $|$ \ 
\href{https://www.linkedin.com/in/qijun-tong/}{\raisebox{-0.05\height}\faLinkedin \ QijunTong} \ \ 
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
%\section{Summary}
%This CV can also be automatically complied and published using GitHub Actions. For details, \href{https://github.com/jitinnair1/autoCV}%{click here}.



%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{University of Electro-communications, Tokyo, Japan} & \hfill Oct 2025 - Now \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Ph.D}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Keio University, Tokyo, Japan} & \hfill Apr 2018 - May 2020 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Master of Engineering}
\end{tabularx}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Keio University, Tokyo, Japan} & \hfill Apr 2014 - May 2018 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Bachelor of Engineering}
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Publications}

Qijun Tong and Kei Kobayashi. Entropy-regularized optimal transport on multivariate normal and
q-normal distributions. \textit{Entropy}, 23(3):302, 2021.


\section{Talks}
\subsection*{Domestic}
1. 童祺俊，小林景 (2018)，"2次元アニメーション制作における中割り自動化のためのベクタ形式画像の対応づけ"，統計関連学会連合大会，中央大学，2018.09
2. 童祺俊 "ガウス過程間のKnothe-Rosenblatt距離について" 第2回：計算技術による学際的統計解析ワークショップ 統計数理研究所 2026.02
3. 童祺俊 "Bernstein過程とその応用" 統計サマーセミナー2025 香川 2025.08

%Experience
\section{Professional experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Data scientist/Optimization Engineer} & \hfill Jun 2023 - present \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Accenture Japan Ltd, Tokyo, Japan}  \\
\end{tabularx}
\begin{itemize}
\item Supervised the development of advanced scheduling algorithms for construction and retail clients, focusing on developing efficient mathematical optimization systems.  

\item Developed proper algorithm, utilized JIT and Cython for performance improvement, and engaged in ETL data modeling, deployment with AWS EKS, and CI/CD environments.  

\item Collaborated with various teams to define testing processes and develop maintenance and operational procedures, ensuring robust and efficient digital transformation solutions.
\end{itemize}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Data scientist/ML Engineer} & \hfill Apr 2020 - May 2023 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{ALBERT, Tokyo, Japan}
\end{tabularx}
\begin{itemize}
\item Led the development and implementation of a social media analysis tool for a securities firm, focusing on designing the analysis architecture and managing data crawling for reputation analysis.  

\item Programmed and introduced a customized Business Intelligence (BI) system. 

\item Conducted R\&D on natural language models to summarize customer complaints for a telecom company, enhancing models with the latest research and fine-tuning them using AWS resources for Proof-of-Concept development.
\end{itemize}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{RIKEN Centre for Advanced Intelligence} & \hfill Apr 2019 - Mar 2020 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Research Assistant (Part-time)}
\end{tabularx}
\begin{itemize}
\item Involved in the research related to the RIKEN Centre’s Mathematical Science team project, assisting with research projects, preparing for conferences, and participating in seminars. 
\end{itemize}

%----------------------------------------------------------------------------------------
%	Languages
%----------------------------------------------------------------------------------------
\section{Languages}
Japanese (Native), English (Intermidiate, IELTS 7.0), Chinese (Conversational)

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\end{tabularx}


\textbf{Mathematical foundations}: a solid foundation in optimization theory, functional analysis, and probability theory. 

\textbf{Technical skills}: Experienced in data processing, machine learning, and mathematical optimization. 

\textbf{Programming skills}:
\begin{itemize}
\item Python (Expert: 5 years): Cupy, Pytorch, Cython, Mixed interger Programming
\item C++ (Intermediate: 3 years): OpenMP, SIMD Instruction: AVX 
\item Rust (Beginner: 1 year): Web assembly
\end{itemize}
\textbf{frameworks}: Microsoft Office, Photoshop, Argo Workflow
\textbf{Cloud platforms}: Amazon AWS, Microsoft Azure
%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Hobbies}
\textbf{Digital illustration}:\href{https://www.deviantart.com/qdsn/gallery}{\faDeviantart Gallery}

\end{document}
